\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{siunitx}
\usepackage{color}

\newcommand{\comments}[1]{}
\newcommand{\xj}[1]{{\color{red}{xj:#1}}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[Siggraph Asia'2018]{ACM SigGraph Asia}{Dec 2018}{Tokyo, Japan}
\acmYear{2018}
%\copyrightyear{2016}


%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}


\begin{document}
\title{Room Layout Estimation from Multi-View Photos}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\comments{
\author{Ruifeng Deng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Science and Technology of China}
  \streetaddress{P.O. Box 1212}
  \city{Hefei}
  \country{China}
  \postcode{43017-6221}
}
\email{trovato@corporation.com}

\author{Chaoyu Xie}
%\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{University of Science and Technology of China}
  \streetaddress{P.O. Box 1212}
  \city{Hefei}
  \country{China}
  \postcode{43017-6221}
}
\email{webmaster@marysville-ohio.com}

\author{Xuejin Chen}
%\authornote{This author is the
%  one who did all the really hard work.}
\affiliation{%
  \institution{University of Science and Technology of China}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hefei}
  \country{China}}
\email{larst@affiliation.org}


% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{B. Trovato et al.}
}

\begin{abstract}
Room layout estimation is a widely explored problem in indoor scene understanding. %While most previous work focus on estimating the room layout in a single-view image, we try to extend the task using multi-view images. 
While room layout estimation in a single-view image has been extensively studied, we take multiple photos as input to better estimate a more complete room layout. 
% 
In this paper, we propose a \xj{more concise} representation of room layout using corners only for convenient integration of multiple views. 
% 
A single-view network (SVNet) is designed to based on the new corner-based representation. 
\xj{The estimated partial layouts for each single view are then stitched together in a simple average manner.}
Our system estimates a more complete room layout with a large field of view, and can be extended to \ang{360}-panoramas. 
The results on a wide range of indoor scenes show the robustness of our method. 
%The results on real data look reasonable and impressive. 
%We also achieve performance close to \ang{360}-panorama-based techniques on a panorama dataset. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010147.10010178.10010224.10010225.10010227</concept_id>
	<concept_desc>Computing methodologies~Scene understanding</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Computing methodologies~Scene understanding}


\keywords{Scene understanding, Layout estimation, Image stitching}


\maketitle

\input{intro}
\input{approach}
\input{results}
%\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
